Global case

### 2025-05-21 lipschitz 2025/Lipitschz.tex
update

	This approach has a similar disadvantage as the model in previous section :the output computed by the network on the optimized inputs may not equal the output value in the solution. Similarly, it is meaningful to compute the upper bound using this approach.

>>>>

	This approach has a similar disadvantage as the model in the previous section: the output computed by the network on the optimized inputs may not equal the output value in the solution. Similarly, it is meaningful to compute the upper bound using this approach.
